---
title: "Floods and Demographics"
author: "Samantha Poteet and Tavio Pela"
date: "12/7/2022"
output:
  xaringan::moon_reader:
    css: ['default', 'metropolis', 'metropolis-fonts', 'css/my-css.css']
    # self_contained: true
    nature:
      highlightStyle: github
      highlightLines: true
      highlightSpans: true
      countIncrementalSlides: false
---
exclude: true

```{r, setup, include = F}
library(knitr)
# Define colors
red_pink   = "#e64173"
turquoise  = "#20B2AA"
orange     = "#FFA500"
red        = "#fb6107"
blue       = "#3b3b9a"
green      = "#8bb174"
grey_light = "grey70"
grey_mid   = "grey50"
grey_dark  = "grey20"
purple     = "#6A5ACD"
slate      = "#314f4f"
# Knitr options
opts_chunk$set(
  comment = "#>",
  fig.align = "center",
  fig.height = 7,
  fig.width = 10.5,
  cache = F,
  warning = F,
  message = F
)
opts_chunk$set(dev = "svg")
options(device = function(file, width, height) {
  svg(tempfile(), width = width, height = height)
})
options(knitr.table.format = "html")
```

---

# Research Question and Motivation 

To what extent is there disproportionate exposure to flood risk based on race and income?

* It is important to understand who is most vulnerable to flooding to determine where aid and infrastructure is needed
* First step to identifying potential inequities in how we address flood risk

* Consequences of Flooding:
  + Fatalities
  + Property damage
  + Contaminate water supplies

---
class: inverse, middle
name: data

# Data

---

# Data

* Demographics and Income Census Data

  + information about what? what is in the data?
  + from?
  + unit of analyisis
  + time period


* FEMA's Nation Flood Hazard Layer (NFHL)

  + This Database includes 32 layers with information on flood insurance rates, control structures, and hazard zones.
  + The data set is provided by the Federal Emergency Management Agency (FEMA)
  + This data is at a refined level with no specific unit. (Smaller than the block level)
  + We use the most up to date version of the data


---
class: inverse, middle
name: data

# Processing


---
# Defining Scope

Broward County, Florida
```{r, echo=FALSE}
#knitr::include_graphics("")
```


---

# Race and Income Data Processing


---

# NFHL Data Processing

* intersection to aggregate up to the tract level

* re-coding choices
  + There 6 different flood hazard zone designations within Broward County
  + We assigned numerical values from 0 to 5 with 5 being the highest risk zone

---
class: inverse, middle
name: analysis

# Findings

---

# Ranked Flood Risk

```{r, echo=FALSE, out.width='60%'}
knitr::include_graphics("/Users/m28t112/Montana State University/Pela, Tavio - Data Analytics Project (1)/output/maps/broward_ranked_fld_hzd.png")
```

---

# Median Household income by tract

```{r, echo=FALSE, out.width='60%'}
knitr::include_graphics("/Users/m28t112/Montana State University/Pela, Tavio - Data Analytics Project (1)/output/maps/broward_median_income.png")
```

---

# Panel
```{r, echo=FALSE, out.width='60%'}
knitr::include_graphics("/Users/m28t112/Montana State University/Pela, Tavio - Data Analytics Project (1)/output/maps/broward_panel_income_fldhzd.png")
```

---

# High Flood Risk Verse Income Scatter

```{r, echo=FALSE}
knitr::include_graphics("/Users/m28t112/Montana State University/Pela, Tavio - Data Analytics Project (1)/output/charts/pctHRsk_by_income.png")
```

---

# Racial/Ethnic tract level Population T

```{r, echo=FALSE}
knitr::include_graphics("/Users/m28t112/Montana State University/Pela, Tavio - Data Analytics Project (1)/output/maps/broward_ethnic_map.png")
```
---

# Demographic Disparities in Flood Risk Bar
```{r, echo=FALSE, out.width='90%'}
knitr::include_graphics("/Users/m28t112/Montana State University/Pela, Tavio - Data Analytics Project (1)/output/charts/bargraph_panel.png")
```

---


```{r, echo=FALSE}
# High Risk versus Percent White
knitr::include_graphics("/Users/m28t112/Montana State University/Pela, Tavio - Data Analytics Project (1)/output/charts/pctHRsk_by_pctWhit.png")

```


---
```{r, echo=FALSE}
# High Risk versus Percent Black
knitr::include_graphics("/Users/m28t112/Montana State University/Pela, Tavio - Data Analytics Project (1)/output/charts/pctHRsk_by_pctBlck.png")

```

---
```{r, echo=FALSE}
# High Risk versus Percent Hispanic (any race)
knitr::include_graphics("/Users/m28t112/Montana State University/Pela, Tavio - Data Analytics Project (1)/output/charts/pctHRsk_by_pctHisp.png")

```

---

class: inverse, middle
name: analysis

# Econometric Models

---

# Motivation

---

# OLS 
```{r, echo=FALSE, , out.width='90%'}
knitr::include_graphics("/Users/m28t112/Montana State University/Pela, Tavio - Data Analytics Project (1)/output/regressions/Table1.png")
```

---

# Linear Probability Model
```{r, echo=FALSE, , out.width='90%'}
knitr::include_graphics("/Users/m28t112/Montana State University/Pela, Tavio - Data Analytics Project (1)/output/regressions/Table2.png")
```

---

# Limitation

---

# The End

Thank you
